Using temperature distributions of active regions to investigate flare activity

### 2015-03-12 paper.tex
References to paper I redone minus brainfart

\subsection{Active region analysis}
The temperature map method described in citetalias{Leonard} was used to investigate the temperatures of the active regions associated with flares which occured during February 2011. % And March, hopefully
This month was chosen because several flares occured during this time with a wide range of peak fluxes. % These months
The flares detected included many small flares (B and C class) as well as several larger M class flares and a single X class flare. % Double check these numbers to include March

>>>>

\subsection{Active region analysis}
The temperature map method described in \citetalias{Leonard} was used to investigate the temperatures of the active regions associated with flares which occured during February 2011. % And March, hopefully
This month was chosen because several flares occured during this time with a wide range of peak fluxes. % These months
The flares detected included many small flares (B and C class) as well as several larger M class flares and a single X class flare. % Double check these numbers to include March
